---
title: "Baseline corrections based on Literature"
author: "Rachel Sjouwerman"
date: "6 4 2021"
output: html_document
---

```{r chunk-options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,            # hide code
  message = FALSE,         # hide messages
  out.width = "80%",
  fig.width = 6,
  fig.asp = 0.618,         # golden ratio betweein height and width  
  dpi = 300
)

```

## Literature search

```{r}
# load libraries
library(ggalluvial)         # for flowchart diagram
library(ggplot2)            # for plotting
library(here)               # for easy path specification
```

```{r}
# read in data
dat <- read.csv(here('files/approach_specifications_extended_factors_2021_04_20.csv'), sep = ';')

# re-order some factor levels
dat$preCS_review <- factor(dat$preCS_review, levels = c('1 s', '2 s', '4 s', '10 s'))
dat$postCS_end_review <- factor(dat$postCS_end_review, levels = c('4.5 s', '5.0 s', '6.0 s', 'CS off', '7.0 s', '8.0 s','CS off + 8.0 s'))

dat$CS_duration <- factor(dat$CS_duration, levels = c('1 s', '4 s', '5 s', '6 s','7 s', '8 s', '10s', '12s'))

dat$postCS_start_review <- factor(dat$postCS_start_review, levels = c('CS on','0.0 s','0.5 s','1.0 s','2.0 s','CS off + 1.0 s', '3.0 s'))

dat$approach_review <- factor(dat$approach_review, levels = c(1:10))
```

Peak at data:

```{r}
head(dat)
str(dat)
```

```{r}
# set specifics 
# save figure
save_fig <- 'no'

# set colors
clrs <-  c("#0000ff",
           "#ffd700",
           "#f15619",
           "#e09fb7",
           "#3f0255")

clrs <- colorspace::sequential_hcl(n = 10, palette = 'Plasma')

# fill title legend
fill_title <- 'pre-CS'
fill_title <- 'approach'

# set font size
size_font <- 30 # for saving fig
size_txt  <- 7
size_font <- 12 # for html
size_txt  <- 2

```

Build flowchart that illustrates what different kind of parameters are used within the baseline correction literature and also how the values specified for these parameters differ across studies.

Four parameters were identified:

-   pre-CS baseline (variable: preCS_review); time window prior to stimulus onset, the mean of the signal within this window is calculated

-   post-CS window start time (variable: postCS_start_review); time after stimulus onset

-   post-CS window end time (variable: postCS_end_review); time after stimulus onset

-   aggregate function applied over signal in post-CS window (variable: max_mean); either maximum value is selected, or mean value is computed

```{r}
# define the marks/ticks along which the flows should pass with axisX

names_stratum <- c("approach", "BLW", "PDW start","PDW end","CS duration","function")

  p_flow_2 <- ggplot(dat, aes(axis1 = approach_review,
                              axis2 = preCS_review,
                              axis3 = postCS_start_review, 
                              axis4 = postCS_end_review,
                              axis5 = CS_duration,
                              axis6 = max_mean)) +
  # plot flow
  geom_alluvium(aes(fill = approach_review), color = 'lightgrey') + # was colored by preCS_review
  # plot the stratums, i.e., bars through which the flow passes
  geom_stratum() +
  # add a label on these stratums
  geom_text(stat = 'stratum', aes(label = after_stat(stratum)), size = size_txt) +
  # change names for ticks on x-axis
  scale_x_discrete(limits = names_stratum, expand = c(.1, .1)) +
  
  #   # add title to plot and change title of legend for the legend type used
  # labs(title = "Flowchart of parameters in reviewed literature for BLC", fill = fill_title
  # ) +
  theme_minimal() +
  # set some layouts
  theme(legend.title = element_text(),
        text = element_text(size=size_font),
        legend.position = 'none') +
    
  # add y-axis title
  ylab('number of studies') +
  # change the colors of the flow
  scale_fill_manual(values = clrs)

# should the figure be saved?
if (save_fig == 'yes'){
  tiff(here('figures/flowchart_BC_literature_2b.tiff'), units="in", width=16, height=12, res=300)
   # jpeg(here('figures/flowchart_BC_literature.jpg'), units="in", width=16, height=12, res=300)
    png(here('figures/flowchart_BC_literature_2c.png'), units="in", width=16, height=12, res=300)
  plot(p_flow_2)
  dev.off()
}
```

Voila, the flowchart:

```{r}
p_flow
```
