---
title: "BC test main effect of task"
author: "Rachel Sjouwerman"
date: "11 2 2021"
output: html_document
---

```{r setup, message = FALSE, warning = FALSE, echo = FALSE}

library(BayesFactor)        # for Bayesian t testing
library(colorspace)         # for colorpalettes
library(dplyr)              # for easy data manipulation
library(ggplot2)            # for plotting
#library(glue)               # for gluing strings to data
library(here)               # for file path
#library(irr)                # for computing reliability between approaches
library(knitr)
#library(lme4)               # for (mixed) linear models
#library(lmerTest)          # for obtaining sig of effects, detach(package:lmerTest, unload=TRUE)
library(patchwork)          # for arranging and labeling plots
#library(sjPlot)             # for putting output mix model in table
library(rstatix)            # for NHST paired-t-test
library(tidyr)              # for swithing between long and wide format
```

```{r chunk-options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,            # hide code
  message = FALSE,         # hide messages
  out.width = "80%",
  fig.width = 6,
  fig.asp = 0.618,         # golden ratio betweein height and width  
  dpi = 300
)

```

```{r}
# Should figures gerenerated in this markdown also be saved?
#save_fig <- 'yes'
save_fig <- 'no'
```

# Introduction

Here, baseline correction approaches are compared in terms of CS discrimination effects. I read in a dataset that contains skin conductance data of the ROFL participants. I used matlab to extract all values (i.e., the parameters that differ between the baseline correction approaches) that are used as input for the baseline correction formula.

The matlab script used to create this data set is named: data/baselineScriptROFL_rachel_temp.m

Description of the variables in this dataset can be found in: \_\_\_\_R_codebook\_\_\_\_\_\_\_

# Analysis for multiverse

Everything needs to be adjusted for the bayesian analyses. I've only done it for the NHST part.

## Prepare data

```{r}
dis_scr <- read.csv(here('data/dis_scr.csv'))
#head(dis_scr)

# I ASSUME THAT: (sabrina needs to check this)
# remove error for approach 11, csm and csp are reversed
df_11 <- dis_scr %>% filter(approach == 11)
names(df_11)[3:4] <- c('csm','csp')
df_11$cs_dis <- (df_11$cs_dis)*-1
dis_scr <- dis_scr[dis_scr$approach != 11,]

df <- merge(dis_scr, df_11, all = T)
dis_scr <- df

# exclude approach 10, in this file it is approach 9 (yoshiike)
dis_scr <- dis_scr %>% filter(approach != 9)
dis_scr[dis_scr$approach == 10, 'approach'] <- 9
dis_scr[dis_scr$approach == 11, 'approach'] <- 10

# note: exclude first trial?
# yes is excluded, i.e., no trial 14 
# compute means over trials
dis_scr_mean <- dis_scr %>% 
  group_by(id, approach) %>%
  summarise(mean_csp = mean(csp,na.rm = T),
            mean_csm = mean(csm,na.rm = T),
            mean_dis = mean_csp - mean_csm) %>%
  data.frame()

names(dis_scr_mean)[3:4] <- c('csp','csm')

# update the type of variables in data
cols_to_factor <- c('id','approach')
dis_scr_mean[,cols_to_factor] <- lapply(dis_scr_mean[,cols_to_factor], as.factor)

# effect size 
dis_scr_mean_long <- pivot_longer(dis_scr_mean, cols = c('csp','csm'), names_to = 'stimType' )
dis_scr_mean_long <- data.frame(dis_scr_mean_long)
dis_scr_mean_long$stimType <- as.factor(dis_scr_mean_long$stimType)

# make csp first factor level
dis_scr_mean_long$stimType <- relevel(dis_scr_mean_long$stimType, 'csp')
```

```{r}
# Read and prepare data
app_param <- read.csv(here('files/approach_specifications.csv'), sep = ';')
names(app_param)[names(app_param) == 'max_mean'] <- 'max1mean0'
# TTP
app_param[app_param$approach == 11, 'preCS'] <- 0
#app_param <- app_param[-11,] # remove TTP scoring from graph

# ACHTUNG HIER DANN AUCH DIE APPROACH NR ANPASSEN
# exclude approach 10, in this file it is approach 9 (yoshiike)
app_param <- app_param %>% filter(approach != 9)
app_param[app_param$approach == 10, 'approach'] <- 9
app_param[app_param$approach == 11, 'approach'] <- 10

# Convert to factor
cols_to_factor <- c('preCS','postCS_start','postCS_end','approach')
app_param[,cols_to_factor] <- lapply(app_param[,cols_to_factor],as.factor)
```

Run t-test

```{r}
t_tests_all <- data.frame()
for(t_model in 1:nlevels(dis_scr_mean$approach)) {
  name_t_test <- paste('t', t_model, sep = '_')
  dat_app <- dis_scr_mean[dis_scr_mean$approach == t_model,]
  dat_app_m <- t.test(dat_app$csp, dat_app$csm, paired = TRUE, alternative = "two.sided")
  assign(name_t_test,dat_app_m)
  #assign(name_t_test, t.test(dat_app$csp, dat_app$csm, paired = TRUE, alternative = "two.sided"))
  
  t_tests_all[t_model,'approach'] <- t_model
  t_tests_all[t_model,'estimate'] <- dat_app_m$estimate
  t_tests_all[t_model,'ci_low']   <- dat_app_m$conf.int[1]
  t_tests_all[t_model,'ci_upp']   <- dat_app_m$conf.int[2]
  t_tests_all[t_model,'t_val']    <- dat_app_m$statistic
  t_tests_all[t_model,'p_val']    <- dat_app_m$p.value
}

```

Run t-test on all 11 approaches. Display results (i.e., effect size) in specification curve.

```{r}
# compute means, wide format
# res_ttest_means <- dat_acq_means %>% filter(stimType %in% c('csp', 'csm')) %>%
#   group_by(approach, preCS, postCS_start, postCS_end,max1mean0) %>%
#   summarise(scr_mean_csp = mean(scr_mean[stimType == 'csp'], na.rm = T),
#             scr_mean_csm = mean(scr_mean[stimType == 'csm'], na.rm = T),
#             scr_sd_csp = sd(scr_mean[stimType == 'csp'], na.rm = T),
#             scr_sd_csm = sd(scr_mean[stimType == 'csm'], na.rm = T))
  
# t test; select csp and csm 
res_ttest <- dis_scr_mean_long %>% filter(stimType %in% c('csp', 'csm')) %>%
  group_by(approach) %>%
  rstatix::t_test(value ~ stimType, data = ., paired = T) 

# effect size
res_ttest_d <- dis_scr_mean_long %>% filter(stimType %in% c('csp', 'csm')) %>%
  group_by(approach) %>%
rstatix::cohens_d(value ~ stimType, data = .,paired = T,ci = T)

# add index to order by effect size
# we have 11 unique approaches
res_ttest_d$approach_num <-  1:nrow(res_ttest_d)
res_ttest_d[order(res_ttest_d$effsize),'approach_eff_order'] <-  1:nrow(res_ttest_d)


# add time window information for 11 appraoches
res_ttest_d <- merge(res_ttest_d, app_param)
```

Run Bayesian t-test on all 120 approaches. Extract effect size for specification curve. Note that the effect size in fact represent something similar as when plotting the BFs. Because the Bayesian t-test tests whether the effect size is different from 0.

```{r}
res_tBF <- list(approach = NA, 
                ttest_BF = NA,
                ttest_BF_post = NA) 

n_appr <- length(levels(dis_scr_mean_long$approach))
for(ind in 1:n_appr){
  # extract name of approach
  appr <- levels(dis_scr_mean_long$approach)[ind]
  
  # build dummy dataframe with one approach only
  dat_dummy <- dis_scr_mean_long %>% filter(stimType %in% c('csp','csm')) %>%
    filter(approach == appr)
  
  # copmute BF (note: when using the formula notation, paired does not work)
  #bf <- ttestBF(formula = scr_mean ~ stimType, data = dat_dummy, paired = T)
  bf <- ttestBF(dat_dummy$scr_mean[dat_dummy$stimType == 'csp'], dat_dummy$scr_mean[dat_dummy$stimType == 'csm'], paired = T)
  bf_post <- posterior(bf, iterations = 1000000)
  
  # put in dataframe
  res_tBF$approach[ind] <- appr
  res_tBF$ttest_BF[ind] <- list(bf)
  res_tBF$ttest_BF_post[ind] <- list(bf_post)
  
}



# extract relevant information from list, build empty dataframe
results_BF_effsize <- data.frame(approach = NA,
                                 approach_num = NA,
                                 effsize = NA,
                                 effsize_low =NA,
                                 effsize_upp = NA,
                                 BF_ln = NA)

for (ind in 1:120){
  results_BF_effsize[ind, 'approach'] <- as.character(res_tBF$approach[ind])
  results_BF_effsize[ind, 'approach_num'] <- ind
  # extract effect size cand 95% interval around effect size
  results_BF_effsize[ind,'effsize'] <- median(res_tBF$ttest_BF_post[[ind]][,'delta'])
  # extract CI around estimate
  results_BF_effsize[ind, 'effsize_low'] <- summary(res_tBF$ttest_BF_post[[ind]])$quantiles['delta',][1]
  results_BF_effsize[ind, 'effsize_upp'] <-summary(res_tBF$ttest_BF_post[[ind]])$quantiles['delta',][4]
  # add log BF
  results_BF_effsize[ind, 'BF_ln'] <- res_tBF$ttest_BF[[ind]]@bayesFactor[['bf']]
}

# add parameters seperately
results_BF_effsize$approach <- factor(results_BF_effsize$approach)
# this is not optimal:
results_BF_effsize <- merge(results_BF_effsize, data.frame(res_ttest[1:5]))

# add column for ordered effect sizes
results_BF_effsize[order( results_BF_effsize$effsize),'approach_eff_order'] <-  1:nrow(results_BF_effsize)
```

Specification curve for regular pairwise t-test.

```{r}
# define colors for plotting
clrs <- c("#ffd700",
"#fa8775",
"#ea5f94",
"#9d02d7",
"#0000ff",
"#2c2c2c")

```

```{r}
# labels
x_lab <- 'approach number ordered by effect size'
y_lab <- 'effect size (Cohen\'s D)'

# order by effect size
# without colors
p0 <- res_ttest_d %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color = approach[1])) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax =conf.high)) +
  scale_color_manual(name = 'paired sample t-test', values = 'black') +
  theme_classic() +
  theme(text = element_text(size=20),
        legend.position = 'top') +
  xlab(x_lab) +
  ylab(y_lab) +
  scale_x_continuous(labels = res_ttest_d$approach_num, breaks = res_ttest_d$approach_eff_order)

# try different colors for categories
p1 <- res_ttest_d %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color = preCS)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  scale_color_manual(name = 'pre-CS time window', values = clrs) +
  theme_classic() +
  theme(text = element_text(size=20),
        legend.position = 'top') +
  xlab(x_lab) +
  ylab(y_lab) +
 scale_x_continuous(labels = res_ttest_d$approach_num, breaks = res_ttest_d$approach_eff_order)

p2 <- res_ttest_d %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color = postCS_start)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  scale_color_manual(name = 'post-CS time window start (ms)', values = clrs) +
  theme_classic() +
  theme(text = element_text(size=20),
        legend.position = 'top') +
  xlab(x_lab) +
  ylab(y_lab) +
  scale_x_continuous(labels = res_ttest_d$approach_num, breaks = res_ttest_d$approach_eff_order)

p3 <- res_ttest_d %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color = postCS_end)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  scale_color_manual(name = 'post-CS time window end (ms)', values = clrs) +
  theme_classic() +
  theme(text = element_text(size=20),
        legend.position = 'top') +
  xlab(x_lab) +
  ylab(y_lab) +
  scale_x_continuous(labels = res_ttest_d$approach_num, breaks = res_ttest_d$approach_eff_order)

p4 <- res_ttest_d %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color =max1mean0)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax =conf.high)) +
  scale_color_manual(name = 'function in post-CS time window', values = clrs) +
  theme_classic() +
  theme(text = element_text(size=20),
        legend.position = 'top') +
  xlab(x_lab) +
  ylab(y_lab) +
 scale_x_continuous(labels = res_ttest_d$approach_num, breaks = res_ttest_d$approach_eff_order)



# plot specifications of BC parameters
s1 <- ggplot(res_ttest_d, aes(x = approach_eff_order, y = preCS, color = preCS)) +
  geom_point(shape = '|', size = 5) +
   scale_color_manual(values = rep('black', length(levels(res_ttest_d$preCS)) )) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none') +
  theme(text = element_text(size=20)) 

s2 <- ggplot(res_ttest_d, aes(x = approach_eff_order, y = postCS_start, color = postCS_start)) +
  geom_point(shape = '|', size = 5) + 
   scale_color_manual(values = rep('black', length(levels(res_ttest_d$postCS_start)) )) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none') +
  theme(text = element_text(size=20)) 

s3 <- ggplot(res_ttest_d, aes(x = approach_eff_order, y = postCS_end, color = postCS_end)) +
  geom_point(shape = '|', size = 5) + 
   scale_color_manual(values = rep('black', length(levels(res_ttest_d$postCS_end)) )) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none') +
  theme(text = element_text(size=20)) 
  
s4 <- ggplot(res_ttest_d, aes(x = approach_eff_order, y = max1mean0, color = max1mean0)) +
  geom_point(shape = '|', size = 5) + 
   scale_color_manual(values = rep('black', length(levels(res_ttest_d$max1mean0)) )) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none') +
  theme(text = element_text(size=20)) +
  ylab('function') 


#ps0 <- p0 / s_all + plot_layout(heights = c(1,3))
ps0 <- p0 / s1 / s2 / s3 / s4  

# plots for supplement, color coded
ps1 <- p1 / (s1 +  scale_color_manual(values = clrs)) / s2 / s3 / s4 
ps2 <- p2 / s1 / (s2 +  scale_color_manual(values = clrs)) / s3 / s4 
ps3 <- p3 / s1 / s2 / (s3 +  scale_color_manual(values = clrs)) / s4 
ps4 <- p4 / s1 / s2 / s3 / (s4 +  scale_color_manual(values = clrs))

if (save_fig == 'yes'){
tiff(here('figures/NHST/spec_curve_lit_search.tiff'), units="in", width=16, height=12, res=300)
plot(ps0 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()

tiff(here('figures/NHST/spec_curve_preCS_lit_search.tiff'), units="in", width=16, height=12, res=300)
plot(ps1 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()

tiff(here('figures/NHST/spec_curve_postCS_start_lit_search.tiff'), units="in", width=16, height=12, res=300)
plot(ps2 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()

tiff(here('figures/NHST/spec_curve_postCS_end_lit_search.tiff'), units="in", width=16, height=12, res=300)
plot(ps3 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()

tiff(here('figures/NHST/spec_curve_meanMax_lit_search.tiff'), units="in", width=16, height=12, res=300)
plot(ps4 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()

}


# actually plot in markdown
#p_spec_curves

```

\

Specification curve for Bayesian effect size.

```{r}
# labels
x_lab <- 'approach number ordered by effect size'
y_lab <- 'effect size (median BF)'

# order by effect size
# without color
p0 <- results_BF_effsize %>%
  ggplot(aes(x = approach_eff_order, y = effsize)) +
  geom_point() +
  geom_errorbar(aes(ymin = effsize_low, ymax =effsize_upp)) +
  theme_classic() +
  xlab(x_lab) +
  ylab(y_lab)

# try different colors for categories


p1 <- results_BF_effsize %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color = preCS)) +
  geom_point() +
    geom_errorbar(aes(ymin = effsize_low, ymax = effsize_upp)) +
#  scale_color_discrete_sequential(palette = "Inferno") +
  #    scale_color_discrete_diverging(palette = "Tropic") +
   scale_color_manual(values = clrs) +
  theme_classic() +
  xlab(x_lab) +
  ylab(y_lab)

p2 <- results_BF_effsize %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color = postCS_start)) +
  geom_point() +
    geom_errorbar(aes(ymin = effsize_low, ymax = effsize_upp)) +
#  scale_color_discrete_sequential(palette = "Inferno") +
  #    scale_color_discrete_diverging(palette = "Tropic") +
  scale_color_manual(values = clrs) +
  theme_classic() +
  xlab(x_lab) +
  ylab(y_lab)

p3 <- results_BF_effsize %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color = postCS_end)) +
  geom_point() +
    geom_errorbar(aes(ymin = effsize_low, ymax = effsize_upp)) +
#  scale_color_discrete_sequential(palette = "Inferno") +
   #   scale_color_discrete_diverging(palette = "Tropic") +
   scale_color_manual(values = clrs) +
  theme_classic() +
  xlab(x_lab) +
  ylab(y_lab)

p4 <- results_BF_effsize %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color =max1mean0)) +
  geom_point() +
  geom_errorbar(aes(ymin = effsize_low, ymax =effsize_upp)) +

 #   scale_color_discrete_divergingx(palette = "Tropic") +
  scale_color_manual(values = clrs) +
  theme_classic() +
  xlab(x_lab) +
  ylab(y_lab)

#p1 + p2 + p3 + p4


# plot specifications of BC parameters
s1 <- ggplot(results_BF_effsize, aes(x = approach_eff_order, y = preCS, color = preCS)) +
  geom_point(shape = '|', size = 5) +
  scale_color_manual(values = rep('black', length(levels(results_BF_effsize$preCS)) )) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none')

s2 <- ggplot(results_BF_effsize, aes(x = approach_eff_order, y = postCS_start, color = postCS_start)) +
  geom_point(shape = '|', size = 5) + 
  scale_color_manual(values = rep('black', length(levels(results_BF_effsize$postCS_start)) )) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none')

s3 <- ggplot(results_BF_effsize, aes(x = approach_eff_order, y = postCS_end, color = postCS_end)) +
  geom_point(shape = '|', size = 5) + 
  scale_color_manual(values = rep('black', length(levels(results_BF_effsize$postCS_end)) )) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none')
  
s4 <- ggplot(results_BF_effsize, aes(x = approach_eff_order, y = max1mean0, color = max1mean0)) +
  geom_point(shape = '|', size = 5) + 
  scale_color_manual(values = rep('black', length(levels(results_BF_effsize$max1mean0)) )) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none') 


s_all <- s1 / s2 / s3 / s4

p0 / s_all + plot_layout(heights = c(1,3))

p1 / s_all + plot_layout(heights = c(1,3))
p1 / s1 / s2 / s3 / s4#+ plot_layout(heights = c(1,3))

# plots for supplement, color coded
p1 / (s1 +  scale_color_manual(values = clrs)) / s2 / s3 / s4 
p2 / s1 / (s2 +  scale_color_manual(values = clrs)) / s3 / s4 
p3 / s1 / s2 / (s3 +  scale_color_manual(values = clrs)) / s4 
p4 / s1 / s2 / s3 / (s4 +  scale_color_manual(values = clrs))
 
 
p_spec_curvesBF <-  (p1 / s_all) +  plot_layout(heights = c(2,1)) | 
  (p2 / s_all) + plot_layout(heights = c(2,1)) | 
  (p3 / s_all) +  plot_layout(heights = c(2,1))| 
  (p4 / s_all) +  plot_layout(heights = c(2,1))

if (save_fig == 'yes'){
 tiff(here('figures/spec_curve_effsizesBF.tiff'), units="in", width=24, height=12, res=450)
plot(p_spec_curvesBF)
dev.off()
}

# actually plot in markdown
#p_spec_curvesBF
```

Make one figure without color to put in manuscript. Color scaled figures are for the supplement.
