---
title: "rank stability"
author: "Rachel Sjouwerman"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, message = FALSE, warning = FALSE, echo = FALSE}


library(dplyr)              # for easy data manipulation
library(ggplot2)            # for plotting
#library(glue)               # for gluing strings to data
library(gridExtra)          # for arranging plots in upp triangle of matrix
library(here)               # for file path
library(irr)                # for computing reliability between approaches
library(knitr)
library(lme4)               # for (mixed) linear models
#library(lmerTest)          # for obtaining sig of effects, detach(package:lmerTest, unload=TRUE)
library(patchwork)          # for arranging and labeling plots
library(tidyr)              # for swithing between long and wide format
library(tidyverse)          # for matching string patterns

#detach("package:plyr", unload=TRUE)
```

```{r chunk-options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,            # hide code
  message = FALSE,         # hide messages
  out.width = "80%",
  fig.width = 6,
  fig.asp = 0.618,         # golden ratio betweein height and width  
  dpi = 300
)

```

```{r Read in data}
# read in Sabrina's data
# file includes 12 approaches (10 BLC, 2 TTP) with scr data per trial (14 CS+, 14 CS-, 14 US)
# data is not log transformed nor range corrected
#dat <- read.csv(here('data/raw_apps_long.csv'))
load(here('data/dfcomplete.Rdata'))
dat <- data.frame(dfcomplete)
rm(dfcomplete)

# clean dataframe
dat <- dat[,c(1:3,7:8)]
names(dat)[3] <- 'number_cs'

# remove approach 9 (Yoshiike)
dat <- dat %>% 
  filter(approach != 9)
# change approach numbers so there is no gap anymore
dat[dat$approach == 10, 'approach'] <- 9
dat[dat$approach == 11, 'approach'] <- 10

# update the type of variables in data
cols_to_factor <- c('id', 'cs', 'approach', 'number_cs')
dat[,cols_to_factor] <- lapply(dat[,cols_to_factor], as.factor)



# add log transformation for scr response
dat <- dat %>% 
  mutate(scr_log = log10(1 + scr))

# add range correction within subject
# note, each approach has its own max per subject
# is it correct that range correction is applied for the acquisition phase only?
dat <- dat %>%
  group_by(id,approach) %>%
  mutate(scr_max = max(scr_log, na.rm = T),           # just to double check max
         scr_log_r = scr_log / max(scr_log, na.rm = T)) %>%
  data.frame()

# get backup of dat, should NA in scr be removed?
dat_backup <- dat 

# note the dfcomplete dataframe already excluded two participants (10, 81)
n_subs <- dat %>%
  pull(id) %>%
  unique() %>%
  length()
```

## Analyses

### Intraclass correlation

First, the strength of agreement -- in other words reliability -- between the various baseline corrections will be evaluated. The scale for skin conductance responding is continuous. Subjects and approaches are viewed as random effects. We want to see whether responses are consistent between BC methods, any systematic differences between approaches are irrelevant, we are not interested in absolute agreement.

```{r Compute reliability estimates}
#dat <- dat_backup


```

### Reliability by Krippendorff

Krippendorff's alpha from the irr package gives approximately the same values as the custom made Krippendorff's alpha from Zapf. They differ only on th 4th or 5th decimal place.

```{r gen-settings-kripp}
# use the function by Zapf to also extract confidence intervals, using bootstrapping
source(here('files/Zapf_Krip_alpha_function.R'))

# set number of bootstrapping, should be 1000, but reduce for testing code
n_boots <- 100
save_dat <- 'yes'
save_fig <- 'yes'
fig_ind <- 2
x_lab <- expression(paste('Krippendorff\'s ',alpha))
y_lab <- 'fear acquisition training trial'
```

First, we will look at the reliability between all (i.e., 9) BLC approaches, excluding TTP.

```{r estimate-reliability-krippendorff-avg}
Sys.time()
# loop through dataframes that only contain one trial (ie.unique cs type and number)

# remove TTP approach (i.e, 10) from dat: approach %in% 1:9
# remove approach 9 (i.e, SCL) for visualisation: approach %in% 1:8 for suppl
dat <- dat %>%
  filter(approach %in% 1:9) %>%
  droplevels()

# split into different dataframes
# 42 acquistition trials
dat_split_per_trial <- dat %>%
  select(id, approach, cs, number_cs, scr) %>% # changed this to scr instead of scr_log_r
  group_split(cs,number_cs)

# build dataframe for extracted data
ka_df <- data.frame(trial = NA,
                    kaZ_rank = NA, 
                    kaZ_rank_lc = NA,
                    kaZ_rank_uc = NA)

# loop through 42 trials (118 subjects * 9 methods = 1380 observations per df)
for (ind in 1:42){
  df <- dat_split_per_trial[[ind]] # trial 1, csm
  
  # dataframe for kripp alpha function from Zapf et al 2016
  df_2 <- df %>% pivot_wider(names_from = approach, values_from = scr, names_prefix = 'approach') %>% # changed this to scr instead of scr_log_r
    select(-c(id,cs,number_cs)) %>%
    as.matrix()
  
  # compute, note nboot is 10 statt 1000, sonst dauert das ewig!
  k_zapf_rank <- k_alpha(df_2, scaling = 'ordinal', nboot = n_boots)
  
  # print(paste(df$cs[1], df$number_cs[1], sep = '_'))
  ka_df[ind,'cs'  ] <-  df$cs[1]
  ka_df[ind,'trial'  ] <-  paste(df$cs[1], df$number_cs[1], sep = '_')
  ka_df[ind, 'kaZ_rank'] <- k_zapf_rank$est.alpha
  ka_df[ind, 'kaZ_rank_lc'] <- k_zapf_rank$ci.boot.alpha[1]
  ka_df[ind, 'kaZ_rank_uc'] <- k_zapf_rank$ci.boot.alpha[2]
  
}
#print values , does the fucntion kable() work here?           
kable(ka_df) 

Sys.time()
```

```{r update-str-df-ka-avg}
# update structure of ka_df
ka_df$trial <- factor(ka_df$trial, levels = ka_df$trial)
ka_df$stimType <- sub('_([^_]*)$','', ka_df$trial)
```

```{r save-ka-avg}
if (save_dat == 'yes'){
 save(ka_df, file = here('data_stats/krippalph_BLC_lit_avg.Rdata')) 
}
```

```{r build-plot-ka-avg}
# plot
p_kA <- ggplot(ka_df, aes(x = kaZ_rank, y = trial, color = stimType)) +
  geom_point(aes(x = kaZ_rank),size = 5) +
  geom_errorbarh(aes(xmin = kaZ_rank_lc, xmax = kaZ_rank_uc), height = 0, size = 1.5) +
  scale_color_manual(name = NULL, values = c('blue','red','black'), labels = c('CS -', 'CS +', 'US'), guide = guide_legend(reverse=TRUE)) +
  xlim(0,1) +
  xlab(x_lab) +
  ylab(y_lab) +
  scale_y_discrete(labels = c('CS_M_1' = '1', 'CS_M_14' = '14',
                              'CS_P_1' = '1', 'CS_P_14' = '14',
                              'US_1' = '1', 'US_14' = '14'), 
                   breaks = c('CS_M_1', 'CS_M_14', 'CS_P_1', 'CS_P_14',
                              'US_1', 'US_14')) +
  # add benchmarks
  geom_vline(xintercept = c(.4, .6, .8), linetype = 'longdash') +
  # add label for benchmarks
  annotate('text', x = .45, y = 42, label = 'fair') +
  annotate('text', x = .65, y = 42, label = 'moderate') +
  annotate('text', x = .85, y = 42, label = 'perfect') +
  theme_classic() +
  theme(text = element_text(size=28), 
        legend.position = c(.15, .95)) 
```

```{r save-ka-avg-plot}
# save fig
if (save_fig == 'yes'){
png(here::here(paste0('figures/fig_', fig_ind, '_krippalph_BLC_lit_avg.png')), units="in", width=16, height=12, res=300)
plot(p_kA)
dev.off()

}
```

Krippendorff's alpha averaged over all BLC approaches:

```{r plot-ka-avg}
p_kA
```

What is the range of Krippendorff's values?

```{r range-val}
min(ka_df$kaZ_rank)
max(ka_df$kaZ_rank)

ka_df %>% dplyr::group_by(cs) %>%
  dplyr::summarise(mean_est = mean(kaZ_rank),
            min_est = min(kaZ_rank),
            max_est = max(kaZ_rank))
```

### Krippendorff average excluding SCL, i.e., only SCR

Compute Krippendorff estimates for only SCR BLC approaches, in other words excluding the approach that focussed on SCL, i.e, approach BLC 9. This information will be presented in the supplement.

```{r estimate-reliability-krippendorff-avg-SCR}
Sys.time()
# loop through dataframes that only contain one trial (ie.unique cs type and number)

# remove TTP approach (i.e, 10) from dat: approach %in% 1:9
# remove approach 9 (i.e, SCL) for visualisation: approach %in% 1:8 for suppl
dat <- dat %>%
  filter(approach %in% 1:8) %>%
  droplevels()

# split into different dataframes
# 42 acquistition trials
dat_split_per_trial <- dat %>%
  select(id, approach, cs, number_cs, scr) %>% # changed this to scr instead of scr_log_r
  group_split(cs,number_cs)

# build dataframe for extracted data
ka_df_SCR <- data.frame(trial = NA,
                    kaZ_rank = NA, 
                    kaZ_rank_lc = NA,
                    kaZ_rank_uc = NA)

# loop through 42 trials (118 subjects * 9 methods = 1380 observations per df)
for (ind in 1:42){
  df <- dat_split_per_trial[[ind]] # trial 1, csm
  
  # dataframe for kripp alpha function from Zapf et al 2016
  df_2 <- df %>% pivot_wider(names_from = approach, values_from = scr, names_prefix = 'approach') %>% # changed this to scr instead of scr_log_r
    select(-c(id,cs,number_cs)) %>%
    as.matrix()
  
  # compute, note nboot is 10 statt 1000, sonst dauert das ewig!
  k_zapf_rank <- k_alpha(df_2, scaling = 'ordinal', nboot = n_boots)
  
  # print(paste(df$cs[1], df$number_cs[1], sep = '_'))
  ka_df_SCR[ind,'cs'  ] <-  df$cs[1]
  ka_df_SCR[ind,'trial'  ] <-  paste(df$cs[1], df$number_cs[1], sep = '_')
  ka_df_SCR[ind, 'kaZ_rank'] <- k_zapf_rank$est.alpha
  ka_df_SCR[ind, 'kaZ_rank_lc'] <- k_zapf_rank$ci.boot.alpha[1]
  ka_df_SCR[ind, 'kaZ_rank_uc'] <- k_zapf_rank$ci.boot.alpha[2]
  
}
#print values , does the fucntion kable() work here?           
kable(ka_df_SCR) 

Sys.time()
```

```{r update-str-df-ka-avg-SCR}
# update structure of ka_df
ka_df_SCR$trial <- factor(ka_df_SCR$trial, levels = ka_df_SCR$trial)
ka_df_SCR$stimType <- sub('_([^_]*)$','', ka_df_SCR$trial)
```

```{r save-ka-avg-SCR}
if (save_dat == 'yes'){
 save(ka_df_SCR, file = here('data_stats/krippalph_BLC_lit_avg_SCR.Rdata')) 
}
```

```{r build-plot-ka-avg-SCR}
# plot
p_kA_SCR <- ggplot(ka_df_SCR, aes(x = kaZ_rank, y = trial, color = stimType)) +
  geom_point(aes(x = kaZ_rank),size = 5) +
  geom_errorbarh(aes(xmin = kaZ_rank_lc, xmax = kaZ_rank_uc), height = 0, size = 1.5) +
  scale_color_manual(name = NULL, values = c('blue','red','black'), labels = c('CS -', 'CS +', 'US'), guide = guide_legend(reverse=TRUE)) +
  xlim(0,1) +
  xlab(x_lab) +
  ylab(y_lab) +
  scale_y_discrete(labels = c('CS_M_1' = '1', 'CS_M_14' = '14',
                              'CS_P_1' = '1', 'CS_P_14' = '14',
                              'US_1' = '1', 'US_14' = '14'), 
                   breaks = c('CS_M_1', 'CS_M_14', 'CS_P_1', 'CS_P_14',
                              'US_1', 'US_14')) +
  # add benchmarks
  geom_vline(xintercept = c(.4, .6, .8), linetype = 'longdash') +
  # add label for benchmarks
  annotate('text', x = .45, y = 42, label = 'fair') +
  annotate('text', x = .65, y = 42, label = 'moderate') +
  annotate('text', x = .85, y = 42, label = 'perfect') +
  theme_classic() +
  theme(text = element_text(size=28), 
        legend.position = c(.15, .95)) 
```

```{r save-ka-avg-plot-SCR}
# save fig
if (save_fig == 'yes'){
png(here(paste0('figures/fig_', fig_ind, '_krippalph_BLC_lit_avg_SCR.png')), units="in", width=16, height=12, res=300)
plot(p_kA_SCR)
dev.off()

}
```

Krippendorff's alpha averaged over all BLC approaches:

```{r plot-ka-avg-SCR}
p_kA_SCR
```

What is the range of Krippendorff's values?

```{r}
min(ka_df_SCR$kaZ_rank)
max(ka_df_SCR$kaZ_rank)
```

#### 

#### Pairwise (i.e, approach wise) comparisons of Krippendorff's alpha

```{r estimate-ka-pairwise}
Sys.time()
# loop through dataframes that only contain one trial (ie.unique cs type and number)

# split into different dataframes
# 42 acquistition trials
dat_split_per_trial <- dat_backup %>%
  select(id, approach, cs, number_cs, scr) %>%
  group_split(cs,number_cs)

# build dataframe for extracted data
ka_df <- data.frame(trial = NA,
                    stimType= NA,
                    kaZ_rank = NA, 
                    kaZ_rank_lc = NA,
                    kaZ_rank_uc = NA,
                    app_x = NA,
                    app_y = NA)
ka_df_pw <- ka_df

# loop through 42 trials (118 subjects * 10 methods = 1180 observations per df, if no NAs in TTP)
for (ind in 1:42){
  df <- dat_split_per_trial[[ind]] # trial 1, csm
  
  # select combinations
  for(app_x in 1:(nlevels(df$approach)-1)){
    for(app_y in (app_x+1):nlevels(df$approach)){
      
      # select 2 approaches to compare, for every subject there are 2 values for the 2 approaches specific stimulus type at this trial, i.e., ideally 118 * 2 values
      df_xy <- df %>%
        filter(approach %in% c(app_x, app_y)) %>%
        droplevels()
      
      
      # dataframe for kripp alpha function from Zapf et al 2016
      df_2 <- df_xy %>% pivot_wider(names_from = approach, values_from = scr, names_prefix = 'approach') %>%
        select(-c(id,cs,number_cs)) %>%
        as.matrix()
      
      # compute, adjust nboot to save time
      # note for all 45 approach comparisons, I set nboot = 1 which does not make sense   for calc a confidence interval off course, bc only 1 value is estimated
      # for 45 (unique approach combinations) and 42 trial = 1890 estimations, this took approx 20 mins to run
      k_zapf_rank <- k_alpha(df_2, scaling = 'ordinal', nboot = n_boots)
      
      # 
      # print(paste(df$cs[1], df$number_cs[1], sep = '_'))
      
      ka_df$trial <-  paste(df$cs[1], df$number_cs[1], sep = '_')
      ka_df$stimType <- as.character(df$cs[1])
      ka_df$kaZ_rank <- k_zapf_rank$est.alpha
      ka_df$kaZ_rank_lc <- k_zapf_rank$ci.boot.alpha[1]
      ka_df$kaZ_rank_uc <- k_zapf_rank$ci.boot.alpha[2]
      ka_df$app_x <- app_x
      ka_df$app_y <- app_y
      
      # put in one large dataframe
      ka_df_pw <- rbind(ka_df_pw, ka_df)
      
    }
  }
}
#print values , does the fucntion kable() work here?           
#kable(ka_df) 

Sys.time()
```

```{r update-str-df}
ka_df_pw <- ka_df_pw[-1, ]  # first row were NAs
ka_df_pw$stimType <- as.factor(ka_df_pw$stimType)
ka_df_pw$trial <- factor(ka_df_pw$trial, levels = unique(ka_df_pw$trial))
ka_df_pw$trial_nr <- factor(gsub('^.*_','',ka_df_pw$trial), levels = 1:14)
#ka_df_pw$app_x <- factor(ka_df_pw$app_x, levels = unique(ka_df_pw$app_x))
#ka_df_pw$app_y <- factor(ka_df_pw$app_y, levels = unique(ka_df_pw$app_y))
```

```{r save-ka-pairs}
if (save_dat == 'yes'){
  save(ka_df_pw, file = here('data_stats/krippalph_BLC_lit_pairwise.Rdata'))
}
```

Now plot Kripp alpha for always two approaches separately for all stimulus types.

```{r settings-plot}
lim_x <- c(-1,1)  # most accurate
lim_x <- c(-.3,1)  # for better data visualisation
```

```{r build-plot-ka-pairwise}
# rename approach 10 to TTP, to avoid confusion
ka_df_pw[ka_df_pw$app_y == 10, 'app_y'] <- 'TTP'

# start with splitting the df per comparison
ka_per_comp <- ka_df_pw %>% 
  group_split(app_x, app_y) 

# 45 comparisons: 9 BLC approaches, 1 TTP method
for (ind in 1:45){
 df_temp <- ka_per_comp[[ind]] %>%
   data.frame()

 plot_ind <- df_temp %>%
   ggplot(aes(x = kaZ_rank, y = trial, color = stimType)) +
   geom_point(aes(x = kaZ_rank)) +
   geom_errorbarh(aes(xmin = kaZ_rank_lc, xmax = kaZ_rank_uc), height = 0.5) +
   scale_color_manual(values = c('blue','red','black')) +
   #xlim(0,1) +
   scale_y_discrete(labels = c('CS_M_1' = '1','CS_M_14' = '14',
                              'CS_P_1' = '1','CS_P_14' = '14',
                              'US_1' = '1','US_14' = '14'), 
                   breaks = c('CS_M_1','CS_M_14','CS_P_1','CS_P_14',
                              'US_1','US_14')) +
    # add benchmarks
  geom_vline(xintercept = c(.4, .6, .8), linetype = 'longdash') +
   scale_x_continuous(n.breaks = 3, limits = lim_x) +
   ggtitle(paste0(df_temp$app_x[1], ' vs ', df_temp$app_y[1])) +
   xlab(x_lab) +
   theme_classic() +
   theme(legend.position = "none",
         text = element_text(size=16) ) +
   theme(axis.title = element_blank())
   # temporary without legend for matrix arrangement

assign(paste('plot_ind',ind, sep = '_'), plot_ind)
}

# combine plots using a matrix
plot_mat <- matrix(nrow = 10, ncol = 10, byrow = T)
plot_ind <- upper.tri(plot_mat, diag = FALSE)
plot_mat[plot_ind] <- c(1,2,10,3,11,18,4,12,19,25,5,13,20,26,31,6,14,21,27,32,36,7,15,22,28,33,37,40,8,16,23,29,34,38,41,43,9,17,24,30,35,39,42,44,45)
#paste0('plot_ind_',1:45,collapse = ',')
plot_list <- list(plot_ind_1,plot_ind_2,plot_ind_3,plot_ind_4,plot_ind_5,plot_ind_6,plot_ind_7,plot_ind_8,plot_ind_9,plot_ind_10,plot_ind_11,plot_ind_12,plot_ind_13,plot_ind_14,plot_ind_15,plot_ind_16,plot_ind_17,plot_ind_18,plot_ind_19,plot_ind_20,plot_ind_21,plot_ind_22,plot_ind_23,plot_ind_24,plot_ind_25,plot_ind_26,plot_ind_27,plot_ind_28,plot_ind_29,plot_ind_30,plot_ind_31,plot_ind_32,plot_ind_33,plot_ind_34,plot_ind_35,plot_ind_36,plot_ind_37,plot_ind_38,plot_ind_39,plot_ind_40,plot_ind_41,plot_ind_42,plot_ind_43,plot_ind_44,plot_ind_45)

# fill matrix with plots
plot_upp_tri <- grid.arrange(grobs = plot_list, layout_matrix = plot_mat) 
```

```{r save-plot-ka-pairwise}
# save plot
if (save_fig == 'yes'){
png(here(paste0('figures/fig_', fig_ind, '_krippalph_BLC_lit_pw.png')), units="in", width=24, height=24, res=300)
plot(plot_upp_tri)
dev.off()
}
```

```{r arrange-ka-plots}
# arrangement with patchwork

# make list of all plots to be plotted
 plot_list_2 <- c(plot_list, list(p_kA))

 # build index of letters for layout of design "matrix"
 letter_ind <- c(rbind(letters[1:26], LETTERS[1:26]))

# hashtags are white space
design <- paste0(paste(letter_ind[1:9], collapse = ''), 
                 '\n', '#', paste(letter_ind[10:17], collapse = ''),
                 '\n', '##', paste(letter_ind[18:24], collapse = ''),
                 '\n', '###', paste(letter_ind[25:30], collapse = ''),
                 '\n', paste(rep(letter_ind[46], 4), collapse = ''), paste(letter_ind[31:35], collapse = ''),
                 '\n', paste(rep(letter_ind[46], 4), collapse = ''), '#', paste(letter_ind[36:39], collapse = ''),
                 '\n', paste(rep(letter_ind[46], 4), collapse = ''), '##', paste(letter_ind[40:42], collapse = ''),
                 '\n', paste(rep(letter_ind[46], 4), collapse = ''), '###', paste(letter_ind[43:44], collapse = ''),
                 '\n', paste(rep(letter_ind[46], 4), collapse = ''), '####', paste(letter_ind[45], collapse = ''))

# plot and add labels
plot_combined <-  wrap_plots(plot_list_2, design = design) +
  plot_layout(tag_level = 'new') +
  plot_annotation(tag_levels = list(c('B', rep('', 44), 'A')))



```

```{r save-ka-combi-plot}
 # save plot
if (save_fig == 'yes'){
png(here(paste0('figures/fig_', fig_ind, '_krippalpha.png')), units="in", width=14, height=12, res=300)
plot(plot_combined)
dev.off()
}
```

```{r pw-TTP-SCL-val}
# update the type of variables in data
cols_to_factor <- c('app_x', 'app_y')
ka_df_pw[,cols_to_factor] <- lapply(ka_df_pw[,cols_to_factor], as.factor)

# compute range for CS+, CS-, and US for pairwise comp SCL - TTP
ka_df_pw %>% 
  dplyr::filter(app_x == '9' & app_y == 'TTP') %>%
  dplyr::group_by(stimType) %>%
  dplyr::summarise(mean_est = mean(kaZ_rank),
            min_est = min(kaZ_rank),
            max_est = max(kaZ_rank)) %>%
  kable(digits = 2)

# compute mean and range for all pairwise comparisons
ka_df_pw %>%
  dplyr::group_by(app_x, app_y, stimType) %>%
  dplyr::summarise(mean_est = mean(kaZ_rank),
            min_est = min(kaZ_rank),
            max_est = max(kaZ_rank)) %>%
  kable(digits = 2)
  
# compute mean and range for all pairwise comparisons; diff order
tab_2 <- ka_df_pw %>%
  dplyr::group_by(app_y, app_x, stimType) %>%
  dplyr::summarise(mean_est = mean(kaZ_rank),
            min_est = min(kaZ_rank),
            max_est = max(kaZ_rank)) %>%
  kable(digits = 2)

t_2 <- ka_df_pw %>%
  dplyr::group_by(app_y, app_x, stimType) %>%
  dplyr::summarise(mean_est = mean(kaZ_rank),
            min_est = min(kaZ_rank),
            max_est = max(kaZ_rank)) 

# extract values for manuscript, SCL vs all other BLC approaches
t_2 %>% filter(app_y == 9) %>%
  group_by(stimType) %>%
  summarise(mean_est = mean(mean_est),
            min_est = min(min_est),
            max_est = max(max_est))

# extrract values for manuscript, TTP vs all  BLC approaches
t_2 %>% filter(app_y == 'TTP') %>%
  group_by(stimType) %>%
  summarise(mean_est = mean(mean_est),
            min_est = min(min_est),
            max_est = max(max_est))
```

### Effect of baseline correction criteria on response

#### Do SCRs differ depending on selected pre-CS window, post-CS window or type of post-CS value (peak/mean)?

SCR \~ preCS \* postCS \* meanMax \* stimulusType

Are there any main effects of interactions. "SCR" refers to the values per stimulus type averaged over all acquisition trials, thus 3 values per subject per approach. If we want to look at this we could also include trial number in the equation.

Next, we will evaluated whether the effect of CS discrimination is different when skin conductance is estimated with different methods the effect will be estimated within each method group and compared with respect to significance (y/n, BF magnitude) and effect size and credible interval.

Sabrina used the criteria from 12 studies in the literature so far. Here the criteria are not systematically varied, and only include a subset of all possibilities. For, illustration, I'll conduct the analysis as far as possible with that subset of data.

```{r}
# # add columns with criterium specifics to the approaches to long data
# head(dat)
# 
# # pre CS time window
# dat[dat$approach %in% 1:3,'preCS'] <- 1
# dat[dat$approach %in% 4:8,'preCS'] <- 2
# dat[dat$approach %in% 9,'preCS'] <- 4
# dat[dat$approach %in% 10,'preCS'] <- 10
# dat[dat$approach %in% 11:12,'preCS'] <- 0
# 
# # start post CS time window
# dat[dat$approach %in% c(3,7,8,10),'postCS_on'] <- 0
# dat[dat$approach %in% c(6),'postCS_on'] <- 0.5
# dat[dat$approach %in% c(1,5),'postCS_on'] <- 1
# dat[dat$approach %in% c(2,9),'postCS_on'] <- 2
# dat[dat$approach %in% c(4),'postCS_on'] <- 3
# dat[dat$approach %in% c(11,12),'postCS_on'] <- 0.9 # TTP, prob doesnt make sense
# 
# # end post CS time window
# dat[dat$approach %in% c(6),'postCS_off'] <- 4.5
# dat[dat$approach %in% c(1,3),'postCS_off'] <- 5
# dat[dat$approach %in% c(4),'postCS_off'] <- 6
# dat[dat$approach %in% c(2,8),'postCS_off'] <- 7
# dat[dat$approach %in% c(5,9),'postCS_off'] <- 8
# dat[dat$approach %in% c(10),'postCS_off'] <- 10
# dat[dat$approach %in% c(7),'postCS_off'] <- 12
# dat[dat$approach %in% c(11,12),'postCS_off'] <- 4 # TTP, prob doesnt make sense
# 
# # add variable approach type: BC vs TTP
# dat$approach_type <- 'BC'
# dat[dat$approach %in% 11:12,'approach_type'] <- 'TTP'
# dat$approach_type <- as.factor(dat$approach_type)
```

```{r}
# # now construct linear model
# lm_1 <- lmer(scr_log_r ~ preCS * postCS_on * postCS_off + (1 | id), dat)
# # using lmertest makes a huge difference here, changes significance, have to look into that what to use
# summary(lm_1)
# anova(lm_1)
# 
# lm_2 <- lmer(scr_log_r ~ approach_type + (1| id),dat)
# 
# # simple rm anova, check contrasts and type (2 or 3)
# aovRM <-  aov(scr_log_r ~preCS*postCS_on*postCS_off + Error(id), dat)
# summary(aovRM)
# 
# aovRM_2 <-  aov(scr_log_r ~ approach + Error(id), dat)
# summary(aovRM_2)
# 
# aovRM_3 <-  aov(scr_log_r ~ approach_type + Error(id), dat)
# summary(aovRM_3)
```

```{r}
# # try some plotting
# #library(emmeans)
# #emmeans(lm_1, list(pairwise ~ preCS ), adjust = "tukey")
# 
# ggplot(dat, aes(x = preCS, y = scr_log_r, group = preCS)) +
#   geom_boxplot()
# 
# ggplot(dat, aes(x = postCS_on, y = scr_log_r, group = postCS_on)) +
#   geom_boxplot()
# 
# ggplot(dat, aes(x = postCS_off, y = scr_log_r, group = postCS_on)) +
#   geom_boxplot()
# 
# ggplot(dat, aes(x = approach_type, y = scr_log_r)) +
#   geom_boxplot()
# 
# ggplot(dat, aes(x = approach, y = scr_log_r)) +
#   geom_boxplot()
# 
# # non log and range corrected data
# ggplot(dat, aes(x = preCS, y = scr, group = preCS)) +
#   geom_boxplot()
# 
# ggplot(dat, aes(x = postCS_on, y = scr, group = postCS_on)) +
#   geom_boxplot()
# 
# ggplot(dat, aes(x = postCS_off, y = scr, group = postCS_on)) +
#   geom_boxplot()
# 
# ggplot(dat, aes(x = approach_type, y = scr)) +
#   geom_boxplot()
# 
# ggplot(dat, aes(x = approach, y = scr)) +
#   geom_boxplot()
# 
# 
# # 
# ggplot(data.frame(dat[dat$id %in% 1:2 & dat$number_cs == 1,]), aes(x = approach, y = scr_log_r,color = cs)) +
#   geom_point() +
#   geom_line(aes(group = id))
```

#### 
