---
title: "BC test main effect of task"
author: "Rachel Sjouwerman"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, message = FALSE, warning = FALSE, echo = FALSE}

library(BayesFactor)        # for Bayesian t testing
library(colorspace)         # for colorpalettes
library(dplyr)              # for easy data manipulation
library(ggplot2)            # for plotting
#library(glue)               # for gluing strings to data
library(here)               # for file path
#library(irr)                # for computing reliability between approaches
library(knitr)
#library(lme4)               # for (mixed) linear models
#library(lmerTest)          # for obtaining sig of effects, detach(package:lmerTest, unload=TRUE)
library(patchwork)          # for arranging and labeling plots
library(plyr)               # for changing factor levels
#library(sjPlot)             # for putting output mix model in table
library(rstatix)            # for NHST paired-t-test
library(tidyr)              # for swithing between long and wide format
```

```{r chunk-options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,            # hide code
  message = FALSE,         # hide messages
  out.width = "80%",
  fig.width = 6,
  fig.asp = 0.618,         # golden ratio betweein height and width  
  dpi = 300
)

```

```{r}
# Should figures gerenerated in this markdown also be saved?
save_fig <- 'yes'
fig_ind <- 3
save_dat <- 'yes'
```

# Introduction

Here, baseline correction approaches are compared in terms of CS discrimination effects. I read in a dataset that contains skin conductance data of the ROFL participants. I used matlab to extract all values (i.e., the parameters that differ between the baseline correction approaches) that are used as input for the baseline correction formula.

The matlab script used to create this data set is named: data/baselineScriptROFL_rachel_temp.m

Description of the variables in this dataset can be found in: \_\_\_\_R_codebook\_\_\_\_\_\_\_

# Analysis for multiverse

## Prepare data

```{r read-data-TTP}
load(here::here('data/TTP2_Claudi_SCR118_PostProcess.Rdata'))

dat_TTP <- claudi
rm(claudi)

# prepare TTP data
head(dat_TTP)
dat_TTP$id <- gsub('B07HH0*','',dat_TTP$id)
dat_TTP <- dat_TTP[c(1:3,5,8)]
names(dat_TTP) <- c('id','stimType','trial','scr','scr_log_rc')

# change names of factor levels for stimType
dat_TTP$stimType <- revalue(dat_TTP$stimType, c(CSM = 'csm', CSP = 'csp', US = 'us'))

detach(package:plyr, unload = T)

# change to factor
cols_to_factor <- c('id', 'trial', 'stimType')
dat_TTP[,cols_to_factor] <- lapply(dat_TTP[,cols_to_factor], as.factor)

# make csp first factor level
dat_TTP$stimType <- relevel(dat_TTP$stimType, 'csp')
```

```{r read-data-multiverse}
# read in data with parameters for baseline corrections
# file includes X approaches with scr data per trial (14 CS+, 14 CS-, 14 US)
# possibly i still have habituation trials in here. Pls check.
# data is not log transformed or range corrected

#120 approaches --> now 200 approaches --> 150 approaches (BLW 4s will be rm (yoshiiki))
#dat <- read.csv(here('data/baseline_corrected_m1_all_subjects.csv'), header = FALSE)
# full data multiverse
dat <- read.csv(here::here('data/baseline_corrected_multiverse_all_subjects.csv'), header = FALSE)

# the matlab file does not have column names
names_cols <- c('id','postCS_start','postCS_end','preCS','max1mean0',	'trial', 'stimulus_type','scr','preCS_val','postCSmean','post_max','onset_postCSmax')
names(dat) <- names_cols
# change nubmers to more indicative labels
#dat[,'stimType'] <- 'csm'
dat[dat$stimulus_type == -1,'stimType'] <- 'csm'
dat[dat$stimulus_type == 1,'stimType'] <- 'csp'
dat[dat$stimulus_type == 999,'stimType'] <- 'us'

# remove column that indicates stimulus type with an unintuitve number
dat <- dat[,-7]

# remove approaches with BW 3s
# remove approaches with BW 4s (yoshiiki)
dat <- dat %>% 
  filter(! preCS %in% c(3000, 4000)) %>%
  droplevels()

# change trial, remove habituation
dat[dat$stimType == 'us','trial'] <- dat[dat$stimType == 'us','trial'] + 7
dat <- dat[dat$trial %in% 8:21,]
dat$trial <- dat$trial - 7

# change levels of max1mean0
dat[dat$max1mean0 == 1, 'max1mean0'] <- 'max'
dat[dat$max1mean0 == 0, 'max1mean0'] <- 'mean'

# update the type of variables in data
cols_to_factor <- c('id','postCS_start','postCS_end','preCS','max1mean0', 'trial', 'stimType')
dat[,cols_to_factor] <- lapply(dat[,cols_to_factor], as.factor)

# add approach variable
dat <- dat %>%
  mutate(approach = factor(paste(preCS,postCS_start, postCS_end, max1mean0, sep ='_')))

# make csp first factor level
dat$stimType <- relevel(dat$stimType, 'csp')
# get backup of dat
dat_backup <- dat 

# exclude subjects 
# VPN 10: Claudia's Mann
# VPN 81: CTQ+ cutoff ueberschritten
dat <- dat %>% filter(!id %in% c(10,81))

# number of subjects in data
n_subs <- dat %>%
  pull(id) %>%
  unique() %>%
  length()
```

```{r data-combine-TTP-multiverse}
# combine BC approaches with TTP approach
# claudi's dataframe contains also 118 pp
dat_TTP <- dat_TTP %>%
  mutate(preCS = 'TTP',
         postCS_start = 'TTP',
         postCS_end = 'TTP',
         max1mean0 = 'TTP',
         preCS_val = NA, 
         postCSmean = NA, 
         post_max = NA,
         onset_postCSmax = NA,
         approach = 'TTP')

dat_TTP <- dat_TTP[,c("id","postCS_start","postCS_end","preCS","max1mean0",       "trial","scr","preCS_val","postCSmean","post_max","onset_postCSmax","stimType", "approach")]
dat <- rbind(dat, dat_TTP)
```

```{r build-acq-df}
# remove first cs+ and first cs- trial (also first US trial)
# compute acquisition means
# note that if package plyr is loaded, this does not work properly!
dat_acq_means <- dat %>% filter(trial != 1) %>%
  group_by(id, stimType, postCS_start, postCS_end, preCS, max1mean0, approach) %>%
  summarise(scr_mean = mean(scr, na.rm = T)) %>%
  data.frame()

n_appr <- length(levels(dat_acq_means$approach))
```

## Specification curve

Run t-test on all 150 BLC approaches and 1 TTP approach. Display results (i.e., effect size) in specification curve.

```{r ttest-NHST}
# compute means, wide format
res_ttest_means <- dat_acq_means %>% filter(stimType %in% c('csp', 'csm')) %>%
  group_by(approach, preCS, postCS_start, postCS_end,max1mean0) %>%
  summarise(scr_mean_csp = mean(scr_mean[stimType == 'csp'], na.rm = T),
            scr_mean_csm = mean(scr_mean[stimType == 'csm'], na.rm = T),
            scr_sd_csp = sd(scr_mean[stimType == 'csp'], na.rm = T),
            scr_sd_csm = sd(scr_mean[stimType == 'csm'], na.rm = T))
  
# t test; select csp and csm 
res_ttest <- dat_acq_means %>% filter(stimType %in% c('csp', 'csm')) %>%
  group_by(approach, preCS, postCS_start, postCS_end,max1mean0) %>%
  rstatix::t_test(scr_mean ~ stimType, data = ., paired = T) 

# effect size
res_ttest_d <- dat_acq_means %>% filter(stimType %in% c('csp', 'csm')) %>%
  group_by(approach, preCS, postCS_start, postCS_end,max1mean0) %>%
rstatix::cohens_d(scr_mean ~ stimType, data = .,paired = T,ci = T)

# add index to order by effect size
# we have n + 1 unique approaches
res_ttest_d$approach_num <-  1:nrow(res_ttest_d)
res_ttest_d[order(res_ttest_d$effsize),'approach_eff_order'] <-  1:nrow(res_ttest_d)
```

Run Bayesian t-test on all 150 BLC approaches and 1 TTP approach. Extract effect size for specification curve. Note that the effect size in fact represent something similar as when plotting the BFs. Because the Bayesian t-test tests whether the effect size is different from 0.

```{r ttest-Bayesian}
n_its <- 100000  # number of iterations, should this be 1000000? Then I run into problems, too big.
res_tBF <- list(approach = NA, 
                ttest_BF = NA,
                ttest_BF_post = NA) 


for(ind in 1:n_appr){
  # extract name of approach
  appr <- levels(dat_acq_means$approach)[ind]
  
  # build dummy dataframe with one approach only
  dat_dummy <- dat_acq_means %>% 
    filter(stimType %in% c('csp','csm')) %>%
    filter(approach == appr)
  
  # copmute BF (note: when using the formula notation, paired does not work)
  #bf <- ttestBF(formula = scr_mean ~ stimType, data = dat_dummy, paired = T)
  bf <- ttestBF(dat_dummy$scr_mean[dat_dummy$stimType == 'csp'], dat_dummy$scr_mean[dat_dummy$stimType == 'csm'], paired = T)
  bf_post <- posterior(bf, iterations = n_its) 
  
  # put in dataframe
  res_tBF$approach[ind] <- appr
  res_tBF$ttest_BF[ind] <- list(bf)
  res_tBF$ttest_BF_post[ind] <- list(bf_post)
  
}



# extract relevant information from list, build empty dataframe
results_BF_effsize <- data.frame(approach = NA,
                                 approach_num = NA,
                                 effsize = NA,
                                 effsize_low =NA,
                                 effsize_upp = NA,
                                 BF_ln = NA)

for (ind in 1:n_appr){
  results_BF_effsize[ind, 'approach'] <- as.character(res_tBF$approach[ind])
  results_BF_effsize[ind, 'approach_num'] <- ind
  # extract effect size cand 95% interval around effect size
  results_BF_effsize[ind,'effsize'] <- median(res_tBF$ttest_BF_post[[ind]][,'delta'])
  # extract CI around estimate
  results_BF_effsize[ind, 'effsize_low'] <- summary(res_tBF$ttest_BF_post[[ind]])$quantiles['delta',][1]
  results_BF_effsize[ind, 'effsize_upp'] <-summary(res_tBF$ttest_BF_post[[ind]])$quantiles['delta',][4]
  # add log BF
  results_BF_effsize[ind, 'BF_ln'] <- res_tBF$ttest_BF[[ind]]@bayesFactor[['bf']]
}

# add parameters seperately
results_BF_effsize$approach <- factor(results_BF_effsize$approach)
# this is not optimal:
results_BF_effsize <- merge(results_BF_effsize, data.frame(res_ttest[1:5]))

# add column for ordered effect sizes
results_BF_effsize[order( results_BF_effsize$effsize),'approach_eff_order'] <-  1:nrow(results_BF_effsize)
```

Specification curve for regular pairwise t-test.

```{r plot-settings}
# set colors for plotting
# set colors
clrs <- colorspace::sequential_hcl(n = 6, palette = 'Plasma')
barplot(1:6, col=clrs)
clrs <- c("#ffd700",
"#fa8775",
"#ea5f94",
"#9d02d7",
"#0000ff",
"#413E3E")

# set sizes 
size_point <- 3  # lines in categories under spec curve
size_text  <- 9 # text and ticks on x and y axis

fig_w <- 8
fig_h <- 5
fig_res <- 300

# change labels for ticks on specification index to seconds, note that if categories change these labels need to be adjusted
labs_bw <- c('1','2','10','TTP') # note that I removed BW: 3s & 4s
labs_pdw_on <- c('0','0.5','1','2','3','TTP')
labs_pdw_off <- c('4.5','5','6','7','8','TTP')
# labs_function <- c('mean','max') # redundant

```

```{r plot-curves}
# labels
x_lab <- 'approach number ordered by effect size'
y_lab <- 'effect size (Cohen\'s D)'

# order by effect size
# without colors
p0 <- res_ttest_d %>%
  ggplot(aes(x = approach_eff_order, y = effsize)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax =conf.high)) +
  theme_classic() +
  theme(text = element_text(size=size_text),
        plot.margin = unit(c(25, 5.5, 5.5, 5.5), "point")) +
  xlab(x_lab) +
  ylab(y_lab) 

# try different colors for categories
# colored by BLW
p1 <- res_ttest_d %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color = preCS)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  scale_color_manual(name = 'BLW', values = clrs[c(-3,-4)], labels = labs_bw) +
  theme_classic() +
  theme(text = element_text(size=size_text),
        legend.position = 'top') +
  xlab(x_lab) +
  ylab(y_lab) + 
  guides(color = guide_legend(nrow = 1))


# colored by 
p2 <- res_ttest_d %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color = postCS_start)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  scale_color_manual(name = 'PDW-start', values = clrs, labels = labs_pdw_on) +
  theme_classic() +
  theme(text = element_text(size=size_text),
        legend.position = 'top') +
  xlab(x_lab) +
  ylab(y_lab) + 
  guides(color = guide_legend(nrow = 1))

p3 <- res_ttest_d %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color = postCS_end)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  scale_color_manual(name = 'PDW-end', values = clrs, labels = labs_pdw_off) +
  theme_classic() +
  theme(text = element_text(size=size_text),
        legend.position = 'top') +
  xlab(x_lab) +
  ylab(y_lab) + 
  guides(color = guide_legend(nrow = 1))

p4 <- res_ttest_d %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color =max1mean0)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax =conf.high)) +
  scale_color_manual(name = 'function', values = clrs[c(1,3,6)]) + # TTP black
  theme_classic() +
  theme(text = element_text(size=size_text),
        legend.position = 'top') +
  xlab(x_lab) +
  ylab(y_lab) + 
  guides(color = guide_legend(nrow = 1))
#p1 + p2 + p3 + p4




```

```{r plot-spec}
# plot specifications of BC parameters
s1 <- ggplot(res_ttest_d, aes(x = approach_eff_order, y = preCS, color = preCS)) +
  geom_point(shape = '|', size = size_point) +
   scale_color_manual(values = rep('black', length(levels(res_ttest_d$preCS)) )) +
  scale_y_discrete(name = 'BLW', labels = labs_bw) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none') +
  theme(text = element_text(size=size_text)) 

s2 <- ggplot(res_ttest_d, aes(x = approach_eff_order, y = postCS_start, color = postCS_start)) +
  geom_point(shape = '|', size = size_point) + 
   scale_color_manual(values = rep('black', length(levels(res_ttest_d$postCS_start)) )) +
    scale_y_discrete(name = 'PDW-start', labels = labs_pdw_on) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none') +
  theme(text = element_text(size=size_text)) 

s3 <- ggplot(res_ttest_d, aes(x = approach_eff_order, y = postCS_end, color = postCS_end)) +
  geom_point(shape = '|', size = size_point) + 
   scale_color_manual(values = rep('black', length(levels(res_ttest_d$postCS_end)) )) +
    scale_y_discrete(name = 'PDW-end', labels = labs_pdw_off) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none') +
  theme(text = element_text(size=size_text)) 
  
s4 <- ggplot(res_ttest_d, aes(x = approach_eff_order, y = max1mean0, color = max1mean0)) +
  geom_point(shape = '|', size = size_point) + 
   scale_color_manual(values = rep('black', length(levels(res_ttest_d$max1mean0)) )) +
    scale_y_discrete(name = 'function') +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none') +
  theme(text = element_text(size=size_text)) 

ps0 <- p0 / s1 / s2 / s3 / s4  

# plots for supplement, color coded
ps1 <- p1 / (s1 +  scale_color_manual(values = clrs[c(-3,-4)])) / s2 / s3 / s4 
ps2 <- p2 / s1 / (s2 +  scale_color_manual(values = clrs)) / s3 / s4 
ps3 <- p3 / s1 / s2 / (s3 +  scale_color_manual(values = clrs)) / s4 
ps4 <- p4 / s1 / s2 / s3 / (s4 +  scale_color_manual(values = clrs[c(1,3,6)]))


```

```{r save-spec-curves-NHST}
if (save_fig == 'yes'){
png(here::here(paste0('figures/fig_', fig_ind, '_curve_cohD.png')), units="in", width=fig_w, height=fig_h, res=fig_res)
plot(ps0 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()

png(here::here(paste0('figures/fig_', fig_ind, '_curve_cohD_BLW.png')), units="in", width= fig_w, height=fig_h, res=fig_res)
plot(ps1 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()

png(here::here(paste0('figures/fig_', fig_ind, '_curve_cohD_PDW_start.png')), units="in", width=fig_w, height=fig_h, res=fig_res)
plot(ps2 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()

png(here::here(paste0('figures/fig_', fig_ind, '_curve_cohD_PDW_end.png')), units="in", width=fig_w, height=fig_h, res=fig_res)
plot(ps3 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()

png(here::here(paste0('figures/fig_', fig_ind, '_curve_cohD_fun.png')), units="in", width=fig_w, height=fig_h, res=fig_res)
plot(ps4 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()

}


# actually plot in markdown
#p_spec_curves
```

\

Specification curve for Bayesian effect size.

```{r plot-curves-BF}
# labels
x_lab <- 'approach number ordered by effect size'
y_lab <- 'effect size (median BF)'

# order by effect size
# without color
# note, I added a dummy color to make sure positions correspond to colored graphs, note II i again removed this and instead changed the margins
p0 <- results_BF_effsize %>%
  ggplot(aes(x = approach_eff_order, y = effsize)) +
  geom_point() +
  geom_errorbar(aes(ymin = effsize_low, ymax =effsize_upp)) +
   theme_classic() +
   theme(text = element_text(size=size_text),
               plot.margin = unit(c(25, 5.5, 5.5, 5.5), "point")) +
  xlab(x_lab) +
  ylab(y_lab) 

# try different colors for categories
p1 <- results_BF_effsize %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color = preCS)) +
  geom_point() +
  geom_errorbar(aes(ymin = effsize_low, ymax = effsize_upp)) +
  scale_color_manual(name = 'BLW',values = clrs[c(-3,-4)], labels = labs_bw) +
  theme_classic() +
  theme(text = element_text(size=size_text),
        legend.position = 'top') +
  xlab(x_lab) +
  ylab(y_lab) + 
  guides(color = guide_legend(nrow = 1))

p2 <- results_BF_effsize %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color = postCS_start)) +
  geom_point() +
    geom_errorbar(aes(ymin = effsize_low, ymax = effsize_upp)) +
  scale_color_manual(name = 'PDW-start', values = clrs, labels = labs_pdw_on) +
  theme_classic() +
  theme(text = element_text(size=size_text),
        legend.position = 'top') +
  xlab(x_lab) +
  ylab(y_lab) + 
  guides(color = guide_legend(nrow = 1))

p3 <- results_BF_effsize %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color = postCS_end)) +
  geom_point() +
    geom_errorbar(aes(ymin = effsize_low, ymax = effsize_upp)) +
   scale_color_manual(name = 'PDW-end', values = clrs, labels = labs_pdw_off) +
  theme_classic() +
   theme(text = element_text(size=size_text),
        legend.position = 'top') +
  xlab(x_lab) +
  ylab(y_lab) + 
  guides(color = guide_legend(nrow = 1))

p4 <- results_BF_effsize %>%
  ggplot(aes(x = approach_eff_order, y = effsize, color =max1mean0)) +
  geom_point() +
  geom_errorbar(aes(ymin = effsize_low, ymax =effsize_upp)) +
  scale_color_manual(name = 'function', values = clrs[c(1,3,6)]) +
  theme_classic() +
   theme(text = element_text(size=size_text),
        legend.position = 'top') +
  xlab(x_lab) +
  ylab(y_lab) + 
  guides(color = guide_legend(nrow = 1))

#p1 + p2 + p3 + p4
```

```{r plot-spec-BF}
# plot specifications of BC parameters
s1 <- ggplot(results_BF_effsize, aes(x = approach_eff_order, y = preCS, color = preCS)) +
  geom_point(shape = '|', size = size_point) +
  scale_color_manual(values = rep('black', length(levels(results_BF_effsize$preCS)) )) +
  scale_y_discrete(labels = labs_bw) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none') +
  theme(text = element_text(size = size_text)) +
  ylab('BLW')

s2 <- ggplot(results_BF_effsize, aes(x = approach_eff_order, y = postCS_start, color = postCS_start)) +
  geom_point(shape = '|', size = size_point) + 
  scale_color_manual(values = rep('black', length(levels(results_BF_effsize$postCS_start)) )) +
  scale_y_discrete(labels = labs_pdw_on) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none') +
  theme(text = element_text(size = size_text)) +
  ylab('PDW-start')

s3 <- ggplot(results_BF_effsize, aes(x = approach_eff_order, y = postCS_end, color = postCS_end)) +
  geom_point(shape = '|', size = size_point) + 
  scale_color_manual(values = rep('black', length(levels(results_BF_effsize$postCS_end)) )) +
  scale_y_discrete(labels = labs_pdw_off) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none') +
  theme(text = element_text(size = size_text)) +
  ylab('PDW-end')
  
s4 <- ggplot(results_BF_effsize, aes(x = approach_eff_order, y = max1mean0, color = max1mean0)) +
  geom_point(shape = '|', size = size_point) + 
  scale_color_manual(values = rep('black', length(levels(results_BF_effsize$max1mean0)) )) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(), 
        axis.ticks.x = element_blank(),
        panel.background = element_blank(),
        legend.position = 'none') +
  theme(text = element_text(size = size_text)) +
  ylab('function') 


# s_all <- s1 / s2 / s3 / s4

# p0 / s_all + plot_layout(heights = c(1,3))

# p1 / s_all + plot_layout(heights = c(1,3))
# p1 / s1 / s2 / s3 / s4#+ plot_layout(heights = c(1,3))

#ps0 <- p0 / s_all + plot_layout(heights = c(1,3))
ps0 <- p0 / s1 / s2 / s3 / s4  

# plots for supplement, color coded
ps1 <- p1 / (s1 +  scale_color_manual(values = clrs[c(-3,-4)])) / s2 / s3 / s4 
ps2 <- p2 / s1 / (s2 +  scale_color_manual(values = clrs)) / s3 / s4 
ps3 <- p3 / s1 / s2 / (s3 +  scale_color_manual(values = clrs)) / s4 
ps4 <- p4 / s1 / s2 / s3 / (s4 +  scale_color_manual(values = clrs[c(1,3,6)]))
 
 
# p_spec_curvesBF <-  (p1 / s_all) +  plot_layout(heights = c(2,1)) | 
#   (p2 / s_all) + plot_layout(heights = c(2,1)) | 
#   (p3 / s_all) +  plot_layout(heights = c(2,1))| 
#   (p4 / s_all) +  plot_layout(heights = c(2,1))

```

```{r save-spec-curves-BF}
if (save_fig == 'yes'){
# 
#  png(here('figures/spec_curve_effsizesBF.tiff'), units="in", width=fig_w, height=fig_h, res=fig_res)
# plot(p_spec_curvesBF)
# dev.off()

png(here(paste0('figures/fig_', fig_ind, '_curve_BFmed.png')), units="in", width=fig_w, height=fig_h, res=fig_res)
plot(ps0 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()

png(here(paste0('figures/fig_', fig_ind, '_curve_BFmed_BLW.png')), units="in", width= fig_w, height=fig_h, res=fig_res)
plot(ps1 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()

png(here(paste0('figures/fig_', fig_ind, '_curve_BFmed_PDW_start.png')), units="in", width=fig_w, height=fig_h, res=fig_res)
plot(ps2 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()

png(here(paste0('figures/fig_', fig_ind, '_curve_BFmed_PDW_end.png')), units="in", width=fig_w, height=fig_h, res=fig_res)
plot(ps3 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()

png(here(paste0('figures/fig_', fig_ind, '_curve_BFmed_fun.png')), units="in", width=fig_w, height=fig_h, res=fig_res)
plot(ps4 + plot_layout(heights = c(2,1,1,1,1)))
dev.off()
}

# actually plot in markdown
#p_spec_curvesBF
```

Save dataframes

```{r save-res-nhst-bf}

if (save_dat == 'yes'){
 save(res_ttest_d, file = here::here('data_stats/results_ttest_nhst.Rdata')) 
 #save(res_tBF, file = here::here('data_stats/results_ttest_bf.txt'))  # need to solve this 
 save(results_BF_effsize, file = here::here('data_stats/results_ttest_eff_bf.Rdata'))
  
}
```

One figure without color is saved to put in manuscript. Color scaled figures combined as gif are for the supplement or online available electronic material.

```{r extract-values-description}
# get some statistics
min(results_BF_effsize$BF_ln)

min(results_BF_effsize$effsize)
max(results_BF_effsize$effsize)
```
