---
title: 'SCR quantification method comparison: Baseline corrections'
author: "Rachel Sjouwerman"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, message = FALSE, warning = FALSE, echo = FALSE}


library(dplyr)              # for easy data manipulation
library(ggplot2)            # for plotting
#library(glue)               # for gluing strings to data
library(here)               # for file path
#library(irr)                # for computing reliability between approaches
library(knitr)
library(lme4)               # for (mixed) linear models
#library(lmerTest)          # for obtaining sig of effects, detach(package:lmerTest, unload=TRUE)
library(patchwork)          # for arranging and labeling plots
#library(plyr)               # for changing factor levels --> calling this directly
library(sjPlot)             # for putting output mix model in table
library(tidyr)              # for swithing between long and wide format
library(viridis)            # for plotting, colors
```

```{r chunk-options, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,            # hide code
  message = FALSE,         # hide messages
  out.width = "80%",
  fig.width = 6,
  fig.asp = 0.618,         # golden ratio betweein height and width  
  dpi = 300
)

```

# Introduction

Here, the effect of the parameters that differ between baseline correction approaches are compared. To start, I will read in a dummy dataset that contains skin conductance data of the first 5 participants. I used matlab to extract all values (i.e., the parameters that differ between the baseline correction approaches) that are used as input for the baseline correction formula.

The matlab script used to create this data set is named: data/baselineScriptROFL_rachel_temp.m

Description of the variables in this dataset can be found in: \_\_\_\_R_codebook\_\_\_\_\_\_\_

# Analysis

## Prepare data

```{r}
save_fig <- 'no'
fig_ind <- 4
```

```{r read-data-multiverse}
# read in data with parameters for baseline corrections
# file includes X approaches with scr data per trial (14 CS+, 14 CS-, 14 US)
# possibly i still have habituation trials in here. Pls check.
# data is not log transformed or range corrected
dat <- read.csv(here::here('data/baseline_corrected_multiverse_all_subjects.csv'), header = FALSE)

# the matlab file does not have column names
names_cols <- c('id','postCS_start','postCS_end','preCS','max1mean0',	'trial', 'stimulus_type','scr','preCS_val','postCSmean','post_max','onset_postCSmax')
names(dat) <- names_cols
# change nubmers to more indicative labels
#dat[,'stimType'] <- 'csm'
dat[dat$stimulus_type == -1,'stimType'] <- 'csm'
dat[dat$stimulus_type == 1,'stimType'] <- 'csp'
dat[dat$stimulus_type == 999,'stimType'] <- 'us'

# remove column that indicates stimulus type with an unintuitve number
dat <- dat[,-7]

# remove approaches with BLW 3s and 4s
dat <- dat %>% 
  filter(! preCS %in% c(3000,4000)) %>%
  droplevels()

# change trial, remove habituation
dat[dat$stimType == 'us','trial'] <- dat[dat$stimType == 'us','trial'] + 7
dat <- dat[dat$trial %in% 8:21,]
dat$trial <- dat$trial - 7

# change levels of max1mean0
dat[dat$max1mean0 == 1, 'max1mean0'] <- 'max'
dat[dat$max1mean0 == 0, 'max1mean0'] <- 'mean'

# update the type of variables in data
cols_to_factor <- c('id','postCS_start','postCS_end','preCS','max1mean0', 'trial', 'stimType')
dat[,cols_to_factor] <- lapply(dat[,cols_to_factor], as.factor)

# add approach variable
dat <- dat %>%
  mutate(approach = factor(paste(preCS,postCS_start, postCS_end,max1mean0, sep ='_')))

# make csp first factor level
dat$stimType <- relevel(dat$stimType, 'csp')
# get backup of dat
dat_backup <- dat 

# exclude subjects 
# VPN 10: Claudia's Mann
# VPN 81: CTQ+ cutoff ueberschritten
dat <- dat %>% filter(!id %in% c(10,81))

# number of subjects in data
n_subs <- dat %>%
  pull(id) %>%
  unique() %>%
  length()
```

```{r read-data-TTP}
load(here::here('data/TTP2_Claudi_SCR118_PostProcess.Rdata'))
dat_TTP <- claudi
rm(claudi)

# prepare TTP data
head(dat_TTP)
dat_TTP$id <- gsub('B07HH0*','',dat_TTP$id)
dat_TTP <- dat_TTP[c(1:3,5,8)]
names(dat_TTP) <- c('id','stimType','trial','scr','scr_log_rc')

# change names of factor levels for stimType
dat_TTP$stimType <- plyr::revalue(dat_TTP$stimType, c(CSM = 'csm', CSP = 'csp', US = 'us'))

#detach(package:plyr, unload = T)

# change to factor
cols_to_factor <- c('id', 'trial', 'stimType')
dat_TTP[,cols_to_factor] <- lapply(dat_TTP[,cols_to_factor], as.factor)

# make csp first factor level
dat_TTP$stimType <- relevel(dat_TTP$stimType, 'csp')
```

Some quick and dirty data visualization of the means of all baseline corrections/separate per baseline correction approach .

```{r plot-means}
# dat_mean <- dat %>%
#   group_by(stimType, trial) %>%
#   summarise(mean_scr = mean(scr, na.rm =T)) %>%
#   data.frame()
# 
# ggplot(dat_mean, aes(x = as.numeric(trial), y = mean_scr, linetype = stimType)) + 
#   geom_point() +
#   geom_line() 
# 
# dat_mean <- dat %>%
#   group_by(stimType, trial, approach) %>%
#   summarise(mean_scr = mean(scr, na.rm =T)) %>%
#   data.frame()
# 
# plot_app <- ggplot(dat_mean, aes(x = as.numeric(trial), y = mean_scr, color = approach, linetype = stimType)) + 
#   geom_point() +
#   geom_line() +
#   theme(legend.position = 'none')
# 
# plot_app


```

## Pre CS value \> Post CS value?

```{r plot-settings}
# set colors
clrs <- c('red','blue','black')
y_lim <- c(0, 5000)
x_lim <- c(-.85, 0.01)
tit_max_panel <- 'SCR (PDW max)'
tit_mean_panel <- 'SCL (PDW mean)'
x_lab <- 'SC < 0 based on BLC'
```

```{r plot-compute-SCR-neg}

# first split for mean or max, and select only negative values
df_max <- dat %>%
  filter(max1mean0 == 'max') %>%
  filter(preCS_val > post_max)

# how many subjects have at least one negative scr?
perc_subs_neg <- df_max %>% pull(id) %>%
  unique() %>%
  length() / n_subs * 100

# number of observations, this should be n subjects x 42 trials x n approaches
# i.e, 118 subjects x 42 trials x 75 max approaches (1/2 of all approaches)
# this is equal for maximum or mean values
n_obs_all <- dat %>%
  filter(max1mean0 == 'max') %>%
  nrow()

n_obs_max <- df_max %>%
  nrow()

# these will be incl in plot
# comp percentage under zero
n_und_zero <- round((n_obs_max / n_obs_all) * 100, 1)

# hoe many of the negative responses, are..
n_csm <- df_max %>%
  filter(stimType == 'csm') %>%
  nrow() / n_obs_max * 100 %>%
  round(digits = 1)

n_csp <- df_max %>%
  filter(stimType == 'csp') %>%
  nrow() / n_obs_max * 100

n_us <- df_max %>%
  filter(stimType == 'us') %>%
  nrow() / n_obs_max * 100

# get descriptive counts from summary table
tit_table <- 'Number of observations per id, the four parameters and stimulus type'
df_max %>% 
  select(id, preCS, postCS_start, postCS_end, max1mean0, stimType) %>%
  summary() %>%
  kable(caption = tit_table)


df_max$stimType <- relevel(df_max$stimType, 'csm')

# make histogram
hist_max <- ggplot(df_max, aes(x = scr, fill = stimType)) +
  geom_histogram(binwidth = 1/500, alpha = .5, position = 'identity') +
  scale_fill_manual(values = clrs, breaks = c('csp','csm','us'), labels = c('CS +','CS -','US')) +

  xlab(x_lab) +
  ylim(y_lim) +
  xlim(x_lim) +
  ggtitle(tit_max_panel) +
     theme(text = element_text(size = 12),
         legend.title = element_blank(),
         plot.title = element_text(hjust = 0.5)) +
  # add percentages text
  annotate('text',label = paste(n_und_zero,'%','< 0',sep = ' '),x = x_lim[1]*.8, y = y_lim[2]) +
  annotate('text',label = paste(round(n_csm,1),'%','CS-',sep = ' '),x = x_lim[1]*.8, y = y_lim[2]*.8, color = 'blue') +
    annotate('text',label = paste(round(n_csp,1),'%','CS+',sep = ' '),x = x_lim[1]*.8, y = y_lim[2]*.7, color = 'red') +
    annotate('text',label = paste(' ',round(n_us,1),' %','US ',sep = ' '),x = x_lim[1]*.8, y = y_lim[2]*.6, color = 'black') 

```

`r round(perc_subs_neg,2)` % of all subjects has at least one negative SCR value.

```{r plot-compute-SCL-neg}
# for mean values
# first split for mean or max
df_mean <- dat %>%
  filter(max1mean0 == 'mean') %>%
  filter(preCS_val > postCSmean)

# how many subjects have at least one negative scr?
perc_subs_neg <- df_mean %>% pull(id) %>%
  unique() %>%
  length() / n_subs * 100

# number of observations, this should be 5 subjects x 42 trials x 60 approaches
# this is equal for maximum or mean values
n_obs_all <- dat %>%
  filter(max1mean0 == 'mean') %>%
  nrow()

n_obs_mean <- df_mean %>%
  nrow()

# these will be incl in plot
n_und_zero <- round((n_obs_mean / n_obs_all) * 100, 1)

n_csm <- df_mean %>%
  filter(stimType == 'csm') %>%
  nrow() / n_obs_mean * 100

n_csp <- df_mean %>%
  filter(stimType == 'csp') %>%
  nrow() / n_obs_mean * 100

n_us <- df_mean %>%
  filter(stimType == 'us') %>%
  nrow() / n_obs_mean * 100

# get descriptive counts from summary table
tit_table <- 'Number of observations per id, the four parameters and stimulus type'
df_mean %>% 
  select(id, preCS, postCS_start, postCS_end, max1mean0, stimType) %>%
  summary() %>%
  kable(caption = tit_table)

df_mean$stimType <- relevel(df_mean$stimType, 'csm')

hist_mean <- ggplot(df_mean, aes(x = scr, fill = stimType)) +
  geom_histogram(binwidth = 1/500, alpha = .5, position = 'identity') +
  scale_fill_manual(values = clrs, breaks = c('csp','csm','us'), labels = c('CS +','CS -','US')) +

  xlab(x_lab) +
  ylim(y_lim) +
 xlim(x_lim) +
    ggtitle(tit_mean_panel) +
    theme(text = element_text(size = 12),
        legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5)) +
    
# add text with percentages
      annotate('text',label = paste(n_und_zero,'%','< 0',sep = ' '),x = x_lim[1]*.8, y = y_lim[2]) +
  annotate('text',label = paste(round(n_csm,1),'%','CS-',sep = ' '),x = x_lim[1]*.8, y = y_lim[2]*.8, color = 'blue') +
    annotate('text',label = paste(round(n_csp,1),'%','CS+',sep = ' '),x = x_lim[1]*.8, y = y_lim[2]*.7, color = 'red') +
    annotate('text',label = paste(' ',round(n_us,1),'%','US ',sep = ' '),x = x_lim[1]*.8, y = y_lim[2]*.6, color = 'black') 



```

```{r plot-combine-SCR-SCL}
hist_max + hist_mean + plot_layout(guides = 'collect') + plot_annotation(tag_levels = 'A')
```

```{r save-combined-SCR-SCL}
# if(save_fig == 'yes'){
#   png(here(paste0('figures/fig_', fig_ind, '_hist_neg_SCR_SCL.png')), units="in", width=8, height=6, res=300)
#   plot(hist_max + hist_mean + plot_layout(guides = 'collect') + plot_annotation(tag_levels = 'A'))
#   dev.off()
# }
```

```{r build-df-neg}
# for all
df_negSCR <- dat %>% 
  filter(scr < 0)
dim(df_negSCR)

#summary(df_negSCR)
```

The value selected in the pre CS time window value (i.e. baseline) occurs to be larger than the value in the postCS time window (here maximum response) quite often. It also happens for all participants. But interestingly it happens only for the CS+ and CS-, not for the US. And also note, that it occurs almost twice as often for CS- as for CS+.

It needs to be checked whether and how this corresponds to TTP scoring and particular the zero responses.

Let's first look at the distribution of the actual BC values, then calculated in these cases:

```{r plot-wrap-try}
# make histogram for all negative SCRs splitted by categorized approaches
ggplot(df_negSCR, aes(x = scr, fill = stimType)) +
  geom_histogram(binwidth = 1/1000, alpha = .5) +
  facet_wrap(.~  max1mean0 )

# df_negSCR %>%
#   filter(max1mean0 == 1) %>%
#   ggplot(aes(x = scr, fill = stimType)) +
#   geom_histogram(binwidth = 1/1000, alpha = .75) +
#   facet_wrap( . ~ preCS )

# plot_hist <- ggplot(df, aes(x = scr, fill = stimType)) +
#  geom_histogram(binwidth = 1/1000, alpha = .5)

```

Bleibt das verhätlnis gleich zwischen CS- und CS+? Wichtig wenn man negativ auf 0 setzen würde.

Wenn auf 0 setzen, ist vermutlich diskriminierung reduziert, weil mehr CS- negativ sind als CS+.

Diskriminiertung cs+ cs- berechnen für diese Fälle

Lineaire verschiebung?

## Run some statistics on frequencies

```{r stats-neg-scr}
df <- dat
df$scr_binair <- ifelse(df$scr < 0, 'negative','positive')

xtabs( ~ df$scr_binair + df$stimType)

# das ist im Grunde ja nichts anderes als so, aufgesplittet für SCR und SCL:
df %>%
  xtabs(~ scr_binair + max1mean0 + stimType, data = .)

# unterscheidet sich die häufigkeit negativer US rekationen pro mean oder max?
# ist das so correct?
df %>% filter(stimType == 'us') %>%
  xtabs( ~ scr_binair + max1mean0, data = .) %>%
  chisq.test() %>%
  apa::chisq_apa()

# pro csp
df %>% filter(stimType == 'csp') %>%
  xtabs( ~ scr_binair + max1mean0, data = .) %>%
  chisq.test() %>%
  apa::chisq_apa()

# pro csm
df %>% filter(stimType == 'csm') %>%
  xtabs( ~ scr_binair + max1mean0, data = .) %>%
  chisq.test() %>%
  apa::chisq_apa()


# unterscheiden sich die häufigkeiten der stimulus typen innerhalb (SCR)
df %>% filter(max1mean0 == 'max') %>%
  xtabs( ~ scr_binair +stimType, data = .) %>%
  chisq.test() %>%
  apa::chisq_apa()

# unterscheiden sich die häufigkeiten der stimulus typen innerhalb (SCL)
df %>% filter(max1mean0 == 'mean') %>%
  xtabs( ~ scr_binair +stimType, data = .) %>%
  chisq.test() %>%
  apa::chisq_apa()


```

## Compare negative values from BLC to TTP values

```{r plot-negBLC-TTP}
# example 
# compare what the values are in TTP scoring
df_max <- df_max %>%
  mutate(stimType_nr = paste(stimType, trial, sep ='_'),
         id_stimType_nr = paste(id, stimType, trial, sep ='_'))

df_mean <- df_mean %>%
  mutate(stimType_nr = paste(stimType, trial, sep ='_'),
         id_stimType_nr = paste(id, stimType, trial, sep ='_'))

dat_TTP <- dat_TTP %>%
  mutate(stimType_nr = paste(stimType, trial, sep ='_'),
         id_stimType_nr = paste(id, stimType, trial, sep ='_'))

# now select all cases from df in dat_TTP
ind_max <- unique(df_max$id_stimType_nr)
ind_mean <- unique(df_mean$id_stimType_nr)

df_TTP_max <- dat_TTP[dat_TTP$id_stimType_nr %in% ind_max,]
df_TTP_mean <- dat_TTP[dat_TTP$id_stimType_nr %in% ind_mean,]

# info for MS
# calculate how many are 0, how many are > 0
#max
n_TTP_resp <- length(df_TTP_max$scr)
n_zero_in_TTP <- sum(df_TTP_max$scr == 0, na.rm = T)
sum(df_TTP_max$scr == 0, na.rm = T) / n_TTP_resp  # % zero responses in TTP
sum(df_TTP_max$scr > 0, na.rm = T) / n_TTP_resp  # % resp > 0 in TTP
sum(is.na(df_TTP_max$scr)) / n_TTP_resp  # % NA in TTP

# per stim type
df_TTP_max_stimType <- df_TTP_max %>% 
  filter(scr == 0) %>%
  group_by(stimType) %>%
  count() %>% 
  data.frame()

# specify zero responses in TTP per stim type
df_TTP_max_stimType <- df_TTP_max_stimType %>%
  mutate(n_perc = n / n_zero_in_TTP)


#mean, info for text MS
n_TTP_resp <- length(df_TTP_mean$scr)
n_zero_in_TTP <- sum(df_TTP_mean$scr == 0, na.rm = T)
sum(df_TTP_mean$scr == 0, na.rm = T) / n_TTP_resp
sum(df_TTP_mean$scr > 0, na.rm = T) / n_TTP_resp
sum(is.na(df_TTP_mean$scr)) / n_TTP_resp
# per stim type
df_TTP_mean_stimType <- df_TTP_mean %>% 
  filter(scr == 0) %>%
  group_by(stimType) %>%
  count() %>%
  data.frame()

# specify zero responses in TTP per stim type
df_TTP_mean_stimType <- df_TTP_mean_stimType %>%
  mutate(n_perc = n / n_zero_in_TTP)

# settings for all plots
y_lim_TTP <- c(0, 1000)
x_lim_TTP <- c(-.1, .75)
bin_w <- 1/100

# relevel
df_TTP_max$stimType <- relevel(df_TTP_max$stimType, 'csm')
df_TTP_mean$stimType <- relevel(df_TTP_mean$stimType, 'csm')

# max
x_lab_TTP <- 'SCR based on TTP for BLC < 0'
hist_max_TTP <- ggplot(df_TTP_max, aes(x = scr, fill = stimType)) +
  geom_histogram(binwidth = bin_w, alpha = .5, position = 'identity') +
  scale_fill_manual(values = clrs, breaks = c('csp','csm','us'), labels = c('CS +','CS -','US')) +
  scale_y_continuous(limits = y_lim_TTP) +
  scale_x_continuous(limits = x_lim_TTP) +
  xlab(x_lab_TTP) +
  theme(text = element_text(size = 12),
        legend.title = element_blank())


# mean
x_lab_TTP <- 'SCR based on TTP for BLC < 0'
hist_mean_TTP <- ggplot(df_TTP_mean, aes(x = scr, fill = stimType)) +
  geom_histogram(binwidth = bin_w, alpha = .5, position = 'identity') +
  scale_fill_manual(values = clrs, breaks = c('csp','csm','us'), labels = c('CS +','CS -','US')) +
  scale_y_continuous(limits = y_lim_TTP) +
  scale_x_continuous(limits = x_lim_TTP) +
  xlab(x_lab_TTP) +
  theme(text = element_text(size = 12),
        legend.title = element_blank())


```

```{r combine-neg-SCR-SCL-BLC-TTP}
# put all plots together
hist_max + hist_mean + hist_max_TTP + hist_mean_TTP + 
  plot_layout(guides = 'collect') + 
  plot_annotation(tag_levels = 'A')
```

```{r save-neg-SCR-SCL-BLC-TTP}
if(save_fig == 'yes'){
  png(here::here(paste0('figures/fig_', fig_ind, '_hist_neg_SCR_SCL_BLC_TTP.png')), units="in", width=8, height=6, res=300)
  plot(hist_max + hist_mean + 
         hist_max_TTP + hist_mean_TTP + 
         plot_layout(guides = 'collect') + 
         plot_annotation(tag_levels = 'A'))
  dev.off()
}
```

```{r stats-neg-SC-in-TTP}

# SCL, do frequencies for stimulus types differ
df_TTP_mean %>% filter(scr == 0) %>%
  xtabs( ~ scr + stimType, data = .) %>%
  chisq.test() %>%
  apa::chisq_apa()

# SCR, do frequencies for stimulus types differ
df_TTP_max %>% filter(scr == 0) %>%
  xtabs( ~ scr + stimType, data = .) %>%
  chisq.test() %>%
  apa::chisq_apa()


```

Thus, what we can infer from these plots (based on these `r n_subs` participants) is that on trials where larger baseline values appear than the post CS values, that in many cases these are scored as zero responses in TTP, but there are also cases where this is not the case.

### Are different peaks detected depending on the post CS time window

Let's plot the onset of the baseline-corrected responses in the post CS time window. We are focusing on the maximum response here, for post CS mean values this is redundant. In total there are 12 combinations of time windows.

```{r response-peak-onset-in-PDW}
# plot onsets of baseline corrected responses based on postCS start and post CS end window

dat$onset_postCSmax_CSrel <- dat$onset_postCSmax + as.numeric(as.character(dat$postCS_start))  # this is not pretty

# change names of factor levels, for nice labels on facet tiles
dat$postCS_start_lab <- plyr::revalue(dat$postCS_start, c('0' = 'CSon', 
        '500' = 'CSon + .5s',
        '1000' = 'CSon + 1s',
        '2000' = 'CSon + 2s',
        '3000' = 'CSon + 3s') )

dat$postCS_end_lab <- plyr::revalue(dat$postCS_end, c('4500' = 'CSoff - 1.5s', 
        '5000' = 'CSoff - 1s',
        '6000' = 'CSoff',
        '7000' = 'CSoff + 1s',
        '8000' = 'CSoff + 2s') )

# make csp first factor level
dat$stimType <- relevel(dat$stimType, 'us') # to start plotting US en overlay with CSs
clrs <- c('red','blue','black') # colors correspond to order in scale fill manual
# plot
plot_onset_max <- dat %>%
  filter(max1mean0 == 'max') %>%
  ggplot(aes(x = onset_postCSmax_CSrel/1000, fill = stimType)) + # /1000 bc ms to s
  geom_histogram(binwidth = .1, alpha = 0.5, position = 'identity') +
  scale_fill_manual(values = clrs, breaks = c('csp','csm','us'), labels = c('CS +','CS -','US')) +
  #scale_color_manual(values = clrs, labels = c('CS +', 'CS -', 'US')) +
  facet_grid(postCS_start_lab ~ postCS_end_lab) +
  xlab('peak detection window (in s)') +
  theme(#strip.background = element_blank(),
 # strip.text.x = element_blank(),
  text = element_text(size=10),
  legend.title = element_blank() 
  #panel.background = element_blank(),
  #panel.grid = element_blank()
  )


# ik vermoed dat de onset_postCSmax waardes nog + the startTimewindow moeten, ik heb dit nu gedaan maar dat moet ik nog in het matlab file terugzoeken. Ik denk namelijk dat de onset betrekking heeft op het tijdpunt van de peak in het tijdwindow en niet op CS onset.


if(save_fig == 'yes'){
  png(here(paste0('figures/fig_', fig_ind, '_SCR_onset_peakvalue.png')), units="in", width=6, height=4, res=300)
plot(plot_onset_max)
dev.off()
}
```

## Regression

```{r regr-test}
# make fact of interest continuous
dat_lm <- dat
dat_lm$postCS_start <- as.numeric(as.character(dat_lm$postCS_start))/1000
dat_lm$postCS_end <- as.numeric(as.character(dat_lm$postCS_end))/1000
dat_lm$preCS <- as.numeric(as.character(dat_lm$preCS))/1000

# RM anova
anovaModelRM <- aov(scr ~ preCS*postCS_start*postCS_end*max1mean0 + Error(id), dat)
summary(anovaModelRM)


# linear mixed model
lmeModel <- lmer(scr ~ preCS*postCS_start*postCS_end*max1mean0 + (1|id), dat)
anova(lmeModel)

# linear mixed model for main effects only
lmeModel_3 <- lmer(scr ~ preCS + postCS_start + postCS_end + max1mean0 + 
                     preCS*stimType + postCS_start*stimType + postCS_end*stimType + max1mean0*stimType +(1|id), dat_lm)
lmeModel_4 <- lmer(scr ~ preCS * postCS_start * postCS_end * max1mean0 * 
                     stimType +(1|id), dat_lm)

lmeModel_5 <- lmer(scr ~ preCS * postCS_start * postCS_end * max1mean0  +(1|id), dat_lm)


lmeModel_6 <- lmer(scr ~ preCS *stimType + postCS_start * stimType + postCS_end * stimType + max1mean0 * stimType  +(1|id), dat_lm)

anova(lmeModel_2)
```

```{r print-table-regr}
tab_model(lmeModel)
tab_model(lmeModel_2)
tab_ind <- 4
tab_model(lmeModel_4, file = here::here(paste0('tables/lme_table_',tab_ind)))
tab_model(lmeModel_6)

```
